Coasting on Duality

### 2024-05-22 duality-presentation.qmd
updated duality presentation

::: {.column width="50%"}
![Correspondence Plot of Southern Women Data Obtained from Simple CA of the Affiliation Matrix](Plots/ca-southern-women.png)
:::
::::

@@

## Reflection Trajectories for SWD
:::: {.columns}
::: {.column width="50%"}
![Person Reflection Trajectories](Plots/p-reflections.png)
:::

::: {.column width="50%"}
![Group Reflection Trajectories](Plots/g-reflections.png)
:::
::::

## Final Reflection Ordering versus CA
:::: {.columns}
::: {.column width="50%"}
![Person Reflection Trajectories](Plots/p-reflections.png)
:::

::: {.column width="50%"}
![Correspondence Plot of Southern Women Data](Plots/ca-southern-women.png)
:::
::::

## Final Reflection Ordering versus CA
:::: {.columns}
::: {.column width="50%"}
![Person Reflection Trajectories](Plots/g-reflections.png)
:::

::: {.column width="50%"}
![Correspondence Plot of Southern Women Data](Plots/ca-southern-women.png)
:::
::::

## Final Reflection Ordering versus CA
:::: {.columns}
::: {.column width="50%"}
![Scatter of standardized person reflection centralities and person scores on first CA dimension (r = 1.0)](Plots/p-ca-ref-corr.png)
:::

::: {.column width="50%"}
![Correspondence Plot of Southern Women Data](Plots/ca-southern-women.png)
:::
::::

## Final Reflection Ordering versus CA
:::: {.columns}
::: {.column width="50%"}
![Scatter of standardized group reflection centralities and group scores on first CA dimension (r = 1.0)](Plots/g-ca-ref-corr.png)
:::

::: {.column width="50%"}
![Correspondence Plot of Southern Women Data](Plots/ca-southern-women.png)
:::
::::

>>>>

::: {.column width="50%"}
![Correspondence Plot of Southern Women Data Obtained from Simple CA of the Affiliation Matrix](Plots/ca-sw.png)
:::
::::

@@

## Reflection Trajectories for SWD
:::: {.columns}
::: {.column width="50%"}
![Person Reflection Trajectories](Plots/p-reflections-sw.png)
:::

::: {.column width="50%"}
![Group Reflection Trajectories](Plots/g-reflections-sw.png)
:::
::::

## Final Reflection Ordering versus CA
:::: {.columns}
::: {.column width="50%"}
![Person Reflection Trajectories](Plots/p-reflections-sw.png)
:::

::: {.column width="50%"}
![Correspondence Plot of Southern Women Data](Plots/ca-sw.png)
:::
::::

## Final Reflection Ordering versus CA
:::: {.columns}
::: {.column width="50%"}
![Person Reflection Trajectories](Plots/g-reflections-sw.png)
:::

::: {.column width="50%"}
![Correspondence Plot of Southern Women Data](Plots/ca-sw.png)
:::
::::

## Final Reflection Ordering versus CA
:::: {.columns}
::: {.column width="50%"}
![Scatter of standardized person reflection centralities and person scores on first CA dimension (r = 1.0)](Plots/p-ca-ref-corr-sw.png)
:::

::: {.column width="50%"}
![Correspondence Plot of Southern Women Data](Plots/ca-sw.png)
:::
::::

## Final Reflection Ordering versus CA
:::: {.columns}
::: {.column width="50%"}
![Scatter of standardized group reflection centralities and group scores on first CA dimension (r = 1.0)](Plots/g-ca-ref-corr-sw.png)
:::

::: {.column width="50%"}
![Correspondence Plot of Southern Women Data](Plots/ca-sw.png)
:::
::::
